### 2018-04-29 paper/design.tex
Replaces some of Adrien's PORs with \acp{SPOR}

This section presents the \name protocol in detail.
Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file $f$ through \name; they start by sharing some information out-of-band, e.g. from their smartphones.
More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.

@@

\begin{figure}[t]
\centering
\def\svgwidth{\columnwidth}
%\input{outline.pdf_tex}
\import{figures/}{outline.pdf_tex}
%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
\caption{\label{fig:outline}Outline of \name's components. Users squads of devices are circled in gray. From top to bottom: a user's devices collaborate through the Squad Overlay; online devices globally share information about them to random peers; using the two above overlays allows for the creation or Predictive Onion Routes (PORs) between sets of devices; secure file exchange between users is enabled by PORs.}
\end{figure}

>>>>

This section presents the \name protocol in detail.
Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file $f$ through \name; they start by sharing some information out-of-band, e.g. from their smartphones.
More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Predictive Onion Route (POR).
PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
From there on, Alice and Bob add the \ac{SPOR} route information to the headers 
of their subsequent file exchange messages, such that the file transfer remains 
secret to anyone but them.

@@

\begin{figure}[t]
\centering
\def\svgwidth{\columnwidth}
%\input{outline.pdf_tex}
\import{figures/}{outline.pdf_tex}
%\includegraphics[width=0.9\columnwidth]{figures/outline.pdf}
\caption{\label{fig:outline}Outline of \name's components. Users squads of 
  devices are circled in gray. From top to bottom: a user's devices collaborate 
  through the Squad Overlay; online devices globally share information about 
  them to random peers; using the two above overlays allows for the creation of 
  \ac{SPOR} routes between sets of devices; secure file exchange between users 
  is enabled by \ac{SPOR}.}
\end{figure}
